Fig1

### 2020-04-18 analysis/figure-1.Rmd
now with better image placement

b <- plottsneelipse(chartsne, chartsne$sex, allcolors)   + labs(y = " ", subtitle = "~ tissue * sex")    
c <- plottsneelipse(ftsne, ftsne$tissue, allcolors ) + labs(y = " ", subtitle = "~ tissue, females only")
d <- plottsneelipse(mtsne, mtsne$tissue, allcolors ) + labs(y = " ", subtitle = "~ tissue, males only")

bcd <- plot_grid(b,c,d, nrow = 1, labels = c("B", "C", "D"), label_size = 8 )
abcd <- plot_grid(a, bcd, nrow = 2, labels = c("A"), label_size = 8, rel_heights = c(1,1))

@@

egi <- plot_grid(e,g,i, nrow = 3, rel_heights = c(1,1,1.4),
                 labels = c("E", "G", "I"), label_size = 8)

@@

fhj <- plot_grid(f,h,j, nrow = 3, rel_heights = c(1,1,1.4),
                 labels = c("F", "H", "J"), label_size = 8)

>>>>

b <- png::readPNG("../figures/images/fig_fig1b.png")
b <- ggdraw() +  draw_image(b, scale = 1)

c <- plottsneelipse(chartsne, chartsne$sex, allcolors)   + labs(y = " ", subtitle = "~ tissue * sex")    
d <- plottsneelipse(ftsne, ftsne$tissue, allcolors ) + labs(y = " ", subtitle = "~ tissue, females only")
e <- plottsneelipse(mtsne, mtsne$tissue, allcolors ) + labs(y = " ", subtitle = "~ tissue, males only")

bcde <- plot_grid(b,c,d,e, nrow = 1, labels = c("B", "C", "D", "E"), label_size = 8 )
abcd <- plot_grid(a, bcde, nrow = 2, labels = c("A"), label_size = 8, rel_heights = c(1,1))

@@

egi <- plot_grid(e,g,i, nrow = 3, rel_heights = c(1,1,1.4),
                 labels = c("F", "H", "J"), label_size = 8)

@@

fhj <- plot_grid(f,h,j, nrow = 3, rel_heights = c(1,1,1.4),
                 labels = c("G", "I", "K"), label_size = 8)
